\cvsection{Experience}

\begin{cventries}
  \cventry
    {Sr. Software Developer} % Job title
    {Hike Messenger} % Organization
    {Delhi} % Location
    {May 2014 - Present} % Date(s)
    {
     \vspace{3pt}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Working in \textbf{core backend team} of hike \textbf{responsible for entire end-to-end backend of messaging} \textbf{for 100+ million users}. Have headed \& \textbf{architected several projects from scratch} from the initial days of hike. Have also \textbf{scaled \& re-architected} several parts of the systems in my tenure to \textbf{handle exponential growth} seen by hike both in terms of \textbf{messaging and number of users}}
		\item {\textbf{Lead the Architecture and Implementation} of the following features' \textbf{end-to-end backend}}
        \begin{cventries}
          \cventry
            {} % Job title
            {} % Organization
            {} % Location
            {} % Date(s)
            {
             \vspace{-20pt}
              \begin{cvsubitems}
                \item {\textbf{Hike Payments} - \textbf{Hike wallet}, integrating merchants like \textbf{Hike Recharge, Zomato}, etc, \textbf{Blue packets} - a fun way of micro-payments, integrating with \textbf{Payment Gateways}, automating \textbf{reconciliation \& settlement}, security \& CS front-end \& tooling}
                \item {\textbf{File Transfer} - with \textbf{pause/resume} via \textbf{chunk uploading}. Further improved the user experience by \textbf{super fast uploading} of existing content via \textbf{MD5}}
		        \item {\textbf{Secondary Message Store} - Brought this concept for \textbf{mass campaigns to optimise storage}. A Redis backed storage layer to deliver campaigns and other low priority messages}
		        \item {\textbf{DX Framework} - A \textbf{zookeeper} based \textbf{Rule Engine} for schedule messages/system packets delivery to the user at D0,D1,DX, etc. at runtime. Rules included specifying device details, new user/returning user checks, upgrade, etc. This empowered PMs in \textbf{feature rollouts \& experiments}}
		        \item {\textbf{User Signup \& Onboarding} - \textbf{OTP \& Missed call} based number verification system for user on-boarding}
		        \item {\textbf{Reward Campaigns} - for user growth which provided \textbf{2X increase in DAU}. The campaigns included rewarding both users by inviting someone on hike, or by performing certain actions (like engaging with other users). \textbf{Integrated} with 3rd party recharge partners like \textbf{PayTM, Oxigen}}
		        \item {\textbf{Pre-activation Service} - to perform \textbf{experiments/monitor \& attribute user behaviour before signup}}
        		\item {\textbf{Multidevice support} - for \textbf{Hike Web}}
        		\item {\textbf{App Migration} - \textbf{Secure \& Seamless Migration} from old to new Hike app}
            	\item {\textbf{Message Tracking Framework} - for \textbf{message reliability}. Working closely with the Data Analysts \& Product managers \& continuously monitoring \& solving user issues around messaging}
              \end{cvsubitems}
            }
        \end{cventries}
		\item {\textbf{Live Database Migrations} - Did the following live DB migrations efficiently with data checks and \textbf{Zero downtime}}
        \begin{cventries}
          \cventry
            {} % Job title
            {} % Organization
            {} % Location
            {} % Date(s)
            {
             \vspace{-20pt}
              \begin{cvsubitems}
                \item {\textbf{Address Book} - Migrated from \textbf{Mysql to HBase} \& subsequently from \textbf{HBase to Big Table (BT)} along with a redis based cache layer}
                \item {\textbf{Timeline's stories} - Migrated from \textbf{HBase to BT}}
                \item {\textbf{Offline Message Store} - Migrated from \textbf{MongoDB to HBase} during live messaging. Users were migrated in batches. This could handle 2X load of the original cluster}
              \end{cvsubitems}
            }
        \end{cventries}
		\item {\textbf{Service Integrations}}
        \begin{cventries}
          \cventry
            {} % Job title
            {} % Organization
            {} % Location
            {} % Date(s)
            {
             \vspace{-20pt}
              \begin{cvsubitems}
                \item {\textbf{Push Notification Service (PNS)} - Integrated with \textbf{APNS(iOS)/FCM(Android)} for proactively reaching client for message delivery \& keeping the \textbf{end-to-end messaging latency low}}
        		\item {\textbf{Cloudinary CDN} - \textbf{Improved client latencies} significantly by \textbf{serving images and videos through CDN}. Earlier implementation included serving through app servers via S3. Also adapted \textbf{network based video quality streaming via CDN} to improve overall user experience}
              \end{cvsubitems}
            }
        \end{cventries}
		\item {\textbf{Micro-Services Architecture}}
        \begin{cventries}
          \cventry
            {} % Job title
            {} % Organization
            {} % Location
            {} % Date(s)
            {
             \vspace{-20pt}
              \begin{cvsubitems}
		        \item {Lead efforts in moving from \textbf{monolith to micro-services} based architecture. \textbf{Exposed lot of micro-services} such as block, friends, Send-Mqtt, Prey, Addressbook \textbf{on thrift} to align with service oriented architecture across teams. \textbf{Converted redundant code to libs} across micro-services.}
              \end{cvsubitems}
            }
        \end{cventries}
      \end{cvitems}
      \vspace{6pt}
    }
%    
%   \cventry
%     {} % Job title
%     {} % Organization
%     {} % Location
%     {} % Date(s)
%     {
%       \begin{cvitems}
%       \end{cvitems}
%     }
  \cventry
    {Software Developer} % Job title
    {BlackNGreen} % Organization
    {Gurgaon} % Location
    {Jul. 2013 - Mar. 2014} % Date(s)
    {
     \vspace{3pt}
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a platform which allows the development of custom IVR(Interactive Voice Response) using drag-n-drop. It is also equipped with a scheduler for OBD(Out Bound Calls).}
      \end{cvitems}
    }
\end{cventries}
